\systemnamenospace: Head Orientation-Based Selection\\in Physical Spaces

### 2014-08-14 doc/sui14/sui14.tex
bjoern's editing pass
Capitalize the first letter of key words

% as we discussed last time, the "Sees" and "Line-of-sight" suggests some computer vision direction 
% need a different title for sure, but not in a hurry
\title{\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces}
%Project GlasSees: Direct Interaction Through Line-of-sight}

@@

\begin{abstract}
\input{abstract}
\end{abstract}
\vspace{-0.05in}
\keywords{
  Wearable computing; spatial interaction; selection; Glass%; infrared
}
\vspace{-0.1in}
%% refer to http://www.acm.org/about/class/ccs98-html
\category{H.5.2.}{Information Interfaces and Presentation (e.g. HCI)}{Interaction styles}% (e.g., commands, menus, forms, direct manipulation).}

@@

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so I choose balance.  See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
%% \balance

>>>>

% as we discussed last time, the "Sees" and "Line-of-sight" suggests some computer vision direction 
% need a different title for sure, but not in a hurry
\title{\systemnamenospace: Head Orientation-Based Selection\\in Physical Spaces}
%Project GlasSees: Direct Interaction Through Line-of-sight}

@@

\begin{abstract}
\input{abstract}
\end{abstract}
%\vspace{-0.05in}
\keywords{
  Wearable Computing; Spatial Interaction; Selection; Glass%; infrared
}
%\vspace{-0.1in}
%% refer to http://www.acm.org/about/class/ccs98-html
\category{H.5.2.}{Information Interfaces and Presentation (e.g. HCI)}{Interaction styles}% (e.g., commands, menus, forms, direct manipulation).}

@@

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so I choose balance.  See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
\balance
